\documentclass[11pt, a4paper ]{article}

\topmargin -1.5cm
\oddsidemargin -0.04cm 
\evensidemargin -0.04cm 
\textwidth 16.59cm 
\textheight 21.94cm 
\parskip 7.2pt 

\begin{document}
\title{Rules and Regulations for Report Styling}
\author{Alex Vorobiev}
\date{\today}
\maketitle

\section{Text}
\begin{itemize}
	\item Don't use \emph{don't}, \emph{can't} or \emph{wouldn't} in official documents.
	\item Try to avoid using the word \emph{basically}. Makes the reader feel stupid.
\end{itemize}

\section{Chapters and Sections}
Please conform to the following rules concerning the structuring and naming of the chapters and sections
\begin{itemize}
	\item All chapters should begin with a small introduction describing the contents.
	\item All titles should be capitalized (i.e. use Capital letters at the start of nouns and verbs).
	\item All sections should have individual .tex files and corresponding labels. Subsections should be labeled with an extra part. For example: chapter - blDO, section - blDOADCS, subsection - blDOADCSActive.
\end{itemize}
\section{Figures}
\begin{itemize}
	\item When referencing in text do it like this: "... figure 4 ..."
	\item Captions should clearly indicate what is shown in the figure.
	\item Labels should be in the form: \emph{fig:blDOname}.
	\item If the image is taken from a website directly, specify the url in the caption in the form: \emph{source: http://www.bla.com }.
	\item B/W compatible.
\end{itemize}
\section{Tables}
\begin{itemize}
	\item Captions: see Figures.
	\item When referencing in text do it like this: "... table 4 ..."
	\item No outside border.
	\item Double line under the column titles.
	\item Column titles in capitals and bold.
	\item Labels should be in the form: \emph{table:blDOname}.
\end{itemize}
\section{Charts}
\begin{itemize}
	\item Black lines.
	\item White bg in boxes (only use color when absolutely necessary, and sparingly).
	\item Do not use color to distinguish things in the captions. Remember that some people print in black/white.
	\item Text: Arial 8pt.
\end{itemize}

\emph{AND MOST IMPORTANTLY: READ WHAT YOU WROTE \textbf{BEFORE} YOU COMMIT IT!}

Check regularly for updates.

\end{document}