\section{Technical Resource Contingencies}
\label{blCont}

When starting the design of a new system the technical resource budgets, like power or mass of the system, are not known yet. They must be estimated based on the information of previous missions, general guidelines and educated estimations. During the design process, the actual budgets will differ from these initial estimations. For example the mass of a satellite will change during the design process because of unexpected problems, changes in the design, etc. To ensure that a product will achieve the required performance while not overspending the budgets, Technical Performance Measurement (TPM) is used. This technique shows the difference between the actual and required performance. For example a contingency of 20$\%$ for the mass budget means that the actual mass can differ up to 20$\%$ of the required mass. TPM establishes contingencies for each technical parameter. This contingency is managed to provide a reserve to spend as the desing difficulties are discovered. The contingency is reduced as the project matures and disappears at the product delivery.

Fortunately, some guidelines exist for contingencies of aerospace vehicles. The main technical resource budgets for our project are mass and power.
Mass and power contingencies are given in tables \ref{tab:masscontingency} and \ref{tab:powercontingency} on page \pageref{tab:masscontingency}.
\begin{landscape}
\begin{table}
\centering
\resizebox{17cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
 & \multicolumn{7}{|c|}{Contingencies $[\%]$}\\ \hline
Design & Propulsion & ADCS & C\&DH & Thermal & Power & Structures \& & Payload \\
maturity & & & & & & Mechanisms & \\ \hline
Conceptual estimate & 20 & 20 & 25 & 20 & 15 & 20 & 20\\ \hline
Layout calculation & 15 & 15 & 20 & 15 & 10 & 15 & 15\\ \hline
Pre-released drawings & 5 & 5 & 10 & 10 & 5 & 5 & 5\\ \hline
Released drawings & 3 & 3 & 5 & 5 & 5 & 3 & 3\\ \hline
Specifications (vendor/subcontractor) & 5 & 5 & 5 & 5 & 5 & 5 & 5\\ \hline
Actual measurement qualification hardware & 1 & 1 & 1 & 1 & 1 & 1 & 1\\ \hline
Actual measurement flight hardware & 0 & 0 & 0 & 0 & 0 & 0 & 0\\ \hline
\end{tabular}
}
\caption{The mass contingency allowance}
\label{tab:masscontingency}
\end{table}

\begin{table}
\centering
\resizebox{17cm}{!}{
\begin{tabular}{|c|c|c|c|c|}
\hline
 & \multicolumn{4}{|c|}{Contingencies $[\%]$}\\ \hline
Design & ADCS & C\&DH & Power & Payload \\
maturity & & & & \\ \hline
Conceptual estimate & 20 & 20 & 15 & 30 \\ \hline
Layout calculation & 15 & 15 & 10 & 20 \\ \hline
Pre-released drawings & 5 & 5 & 5 & 10 \\ \hline
Released drawings & 3 & 3 & 5 & 5 \\ \hline
Specifications (vendor/subcontractor) & 5 & 5 & 5 & 5 \\ \hline
Actual measurement qualification hardware & 1 & 1 & 1 & 1\\ \hline
Actual measurement flight hardware & 0 & 0 & 0 & 0 \\ \hline
\end{tabular}}
\caption{The power contingency allowance}
\label{tab:powercontingency}
\end{table}
\end{landscape}