\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Before you lies the final report on our evaluation of the feasibility of the \acf{FLAMeS} concept. It has been a pleasure to work on it these weeks, and it is with some pride and with great satisfaction that I present to you the result of our hard work.\\\\
This is also the place to thank those who have been so kind as to give us some of their precious time.

First I want to mention professor Edoardo Charbon, who kindly explained and showed to us the workings of his \ac{SPAD}\footnote{See \cite[98-105]{SPADThesis}, \cite{SPAD2} and \cite{SPAD3}}: without his help we would be hopelessly in the dark on these fascinating devices. From this place I also want to thank professor Kourosh Khoshelham for helping us to some valuable material on remote sensing. I also want to thank Jasper Bouwmeester, who provided us with some helpful information on solar panel pricing.

I would also like to thank Diego Kennis and Hein Vos from Minimotor/Faulhauber for the information and cost estimation they provided for the motors we considered. Furthermore I would like to thank Kees de Boom from TNO for providing us with some information on sun sensor pricing and for pointing out some helpful considerations. Finally I would like to thank Jeroen Rotteveel from ISIS for providing us with the prices of their sun sensor and star tracker.

And finally I thank our tutor, professor Ben Gorte, who was very generous to us with his time and has been very supportive of the entire project.\\\\
I hope you will have as much fun reading this report, as we had in making it!\\\\
Yours sincerely,\\\\\\\\
 \hspace{2cm}Co Florijn,\\
 \hspace{2cm}Chairman