In February 2010 the ICESat mission ended after 7 years of measuring ice sheet mass balance, cloud and aerosol heights, as well as land topography and vegetation characteristics.
To do all this, ICESat had only one instrument on board: a space based \ac{LiDAR} system (\ac{GLAS}), allowing for an unprecedented 3D view of the Earth's surface and atmosphere.
The laser lifetimes, however, were severely limited because of manufacturing errors in one of the laser components.

ICESat followed only one of the possible approaches for \ac{LiDAR}, namely the use of a high energy laser and a large receiver telescope. The other approach is using a high frequency, low energy laser and a single photon detector. The advantage of the latter approach is that it has a much lower mass, but it is uncertain if even a single photon per pulse reaches the receiver. One possible solution could be the use of a swarm of satellites around the emitter, each equipped with a single photon detector. However the technical feasibility of this concept has not yet been proven.

In this mid term review some options for this concept are proposed and traded off so as to find the best fit for the mission. This tradeoff is what the bulk of this report is about. Also described are the workings and results from the simulator, as well as the project and risk management. Chapters on operation and logistics, stability and control and sustainability are included too.

% Chapter \ref{blFuncChapter} describes the functions and requirements of the system as a whole, whereas Chapter \ref{blBudgets} shows the multiple budget breakdowns and resource allocation. In Chapter \ref{blRisk} the technical risks are investigated. Chapter \ref{blDesignOptions} illustrates the different design options. Since sustainable engineering is an important factor, Chapter \ref{blSustainable} is devoted to this subject. In Chapter \ref{blInvestment} the return on investment and operational profit are discussed and finally in Chapter \ref{blRAMS1} the \ac{RAMS} are studied.